Computing with cut systems +

### 2015-10-18 cutsystems-new.tex
Edits.

% Commands
\def\Res{\res\!}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\Ress}[1]{\res_{#1}\!}
\newcommand{\cat}[1]{\mathcal{#1}}
\newcommand{\lto}{\longrightarrow}
\newcommand{\xlto}[1]{\stackrel{#1}\lto}
\newcommand{\mf}[1]{\mathfrak{#1}}
\newcommand{\md}[1]{\mathscr{#1}}
\def\l{\,|\,}
\def\sgn{\textup{sgn}}

@@

\begin{abstract}
In the bicategory of Landau-Ginzburg models $\LG$ the objects are certain polynomials called potentials, and the $1$-morphisms are matrix factorisations. The composition of these $1$-morphisms is defined by a form of convolution, and is not easy to compute. In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms is given explicitly. This construction will be applied in a sequel to define an enrichment of $\LG$ over affine schemes.
\end{abstract}

@@

If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise the possible matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$ whose coordinates are the coefficients of the various monomials in each row and column of $D$. Hence as sets we have
\begin{equation}\label{eq:param_frmf}
\LG(W,V)_{fin} = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)_{\nC}\,.
\end{equation}
For various applications, two of which we sketch below, we would like to know that the basic operations of the bicategory $\LG$ respect this additional scheme structure; that is, that these operations are continuous in the coordinates which parametrise the $1$-morphisms. The most important and nontrivial such structure is the composition functor
\begin{gather*}
\LG(V,U)_{fin} \times \LG(W, V)_{fin} \lto \LG(W,U)\,,\\
(Y,X) \mapsto Y \otimes X\,.
\end{gather*}
We would like therefore to produce a morphism of schemes (omitting indices)
\[
c: \mathscr{M}(V,U) \times \mathscr{M}(W,V) \lto \mathscr{M}(W,U)
\]
with the property that $c([Y], [X]) = [Y \otimes X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.

The problem is that this doesn't make any sense, because $Y \otimes X$ contains monomials $x^i y^j z^k$ with $y$'s in them (we say $Y \otimes X$ is \emph{infinite rank} over $k[x,z]$) and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$. However one can prove that $Y \otimes X$ is a summand in the homotopy category of a finite rank matrix factorisation (involving only $x$'s and $z$'s) and even describe this object and the corresponding idempotent explicitly \cite{dm1102.2957}. This is a finite amount of data which can be used to encode $Y \otimes X$, so we just need to replace $\mathscr{M}(W,U)$ by some scheme which knows how to store such data.

@@

After some refinements\footnote{See Remark \ref{remark:relation_to_toby_paper} for a discussion of why we end up encoding the finite model by Clifford actions rather than the idempotents of \cite{dm1102.2957}.} this amounts to replacing $\LG$ by an equivalent bicategory $\cat{L}$ with the same objects and (almost) the same $1$-morphisms, but whose composition operation is easily encoded as a morphism of schemes. We say \emph{almost} the same $1$-morphisms because in $\cat{L}$ the $1$-morphisms are still finite rank matrix factorisations, but now they may additionally equipped with the action of a Clifford algebra. It remains straightforward to parametrise these $1$-morphisms by the closed points of an affine scheme, but in contrast to $\LG$ the composition functor in $\cat{L}$ (which we refer to as the \emph{cut operation})
\begin{gather}
\cat{L}(V,U) \times \cat{L}(W,V) \lto \cat{L}(W,U)\,,\\
(Y,X) \mapsto Y \l X
\end{gather}
does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal. The schemes parametrising $1$-morphisms in $\cat{L}$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}. However the present paper is concerned only with defining the bicategory $\cat{L}$ and proving that it is equivalent to $\LG$.

The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory. In Section \ref{section:cut_systems} we define cut systems and the superbicategory associated to a cut system, then we construct the cut model of $\LG$ in Section \ref{section:lg_cut_system}.

@@

The bicategory $\LG$ arises in topological field theory (TFT) as the data necessary to define a two-dimensional topological field theory with defects \cite{k1004.2307,dkr1107.0495}. It is expected that such a TFT should be associated to any suitably nice bicategory $\cat{B}$. In the formalisation of \cite[\S 3.1]{dkr1107.0495} the associated TFT is a symmetric monoidal functor
\[
\mathcal{Z}: \operatorname{Bord}_{2,1} \lto \operatorname{Vect}_\nC
\]
where the objects of $\operatorname{Bord}_{2,1}$ are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.

\begin{figure}[bt]
$$
  \raisebox{-75pt}{\begin{picture}(300,130)
  \put(0,0){\scalebox{0.6}{\includegraphics{pic02.eps}}}
  \put(0,0){
     \setlength{\unitlength}{.55pt}\put(-22,-8){
%     \put(136,224)   {$ \phi_\text{in} $}
%     \put(140, 22)   {$ \phi_\text{in} $}
%     \put(433,142)   {$ \phi_\text{out} $}
	 \put(295,85)   {$ Y $}
	 \put(240,190)   {$ X $}
     \put(510,180)   {$ O_{3} $}
     \put( 10,230)   {$ O_{1} $}
     \put( 10,110)   {$ O_{2} $}
     }\setlength{\unitlength}{1pt}}
  \end{picture}}
$$
\caption{A world-sheet $M$ with defect lines from $\,(O_1,O_2)\,$ to
$\,(O_{3})$.\ The two-dimensional regions of the world-sheet are all labelled with the same potential $W(x)$, while $X,Y$ are matrix factorisations of $W(x) - W(x')$. The labels on the other defect lines are omitted.}
\label{fig:wsh-defect}
\end{figure}

Consider the example shown in Figure \ref{fig:wsh-defect}, where $\cat{B} = \LG$, the two-dimensional regions are all labelled with a single potential $W(x)$ and $X,Y: W \lto W$ are $1$-morphisms. The value of $\mathcal{Z}$ on $M$ is a $\nC$-linear map
\be\label{eq:value_of_bordism}
\mathcal{Z}(M): \mathcal{Z}(O_1) \otimes \mathcal{Z}(O_2) \lto \mathcal{Z}(O_3)\,.
\ee
We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$. Namely, it is a consequence of the way the defect conditions $X,Y$ enter the partition function \cite[(3.16)]{laz} that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining $Y,X$. To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme $\mathscr{M}_Y \times \mathscr{M}_X$ parametrising possible labels and $\mathcal{Z}(M)$ as a morphism of these vector bundles. But there are some obstacles.
% \cite[(2.9)]{dkr1107.0495}

Consider the incoming circle $O_2$ with its labels $Y,X$. The construction gives
\be\label{eq:zo2orig}
\mathcal{Z}(O_2) := H^0 \Hom_{\nC[x,x']}( Y, X )
\ee
which is the vector space of $2$-morphisms $Y \lto X$ in $\LG(W,W)$. Now suppose that the defect conditions are made to depend on parameters 
\[
Y = Y(t_1,\ldots,t_r)\,, \qquad X = X(u_1,\ldots,u_s)
\]
which satisfy their own equations and cut out a parametrising scheme $\mathscr{M}_Y \times \mathscr{M}_X \subseteq \mathbb{A}^{r+s}$. The question is: what kind of global object $\mathcal{Z}(O_2)$ on $\mathscr{M}_Y \times \mathscr{M}_X$ is formed by the finite-dimensional vector spaces
\[
\mathcal{Z}(O_2)_{P,Q} := H^0 \Hom_{\nC[x,x']}( Y(P), X(Q) )
\]
as $P$ varies over $\mathscr{M}_Y$ and $Q$ over $\mathscr{M}_X$? The problem is that \emph{a priori} we have
\be\label{eq:cohom_sucks}
\big\{ H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \big\}_{P,Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
\ee
%This is a particular case of a general phenomenon: any complex of $\nC$-vector spaces $C$ is isomorphic in the derived category $\mathbb{D}(\nC)$ to $\bigoplus_n H^n(C)[n]$, but over a general ring, for instance the coordinate ring of $\mathscr{M}_Y \times \mathscr{M}_X$, this is not the case. 
The solution is to work instead with the full complex, which suggests the definition\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
\be\label{eq:wuhe20}
\mathcal{Z}(O_2) := \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \in \mathbb{D}( \operatorname{qcoh} \mathscr{M}_Y \times \mathscr{M}_X )\,.
\ee
An alternative (and we believe simpler) approach is to take $\cat{L}$ rather than $\LG$ as the input to the definition of the TFT. Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define $\mathcal{Z}(O_2)$ to be the following composite in $\LG$:
\be\label{eq:composite_intro_o2}
\xymatrix@C+2pc{
0 \ar[r]^-X & W(x) - W(x') \ar[r]^-{Y^{\vee}} & 0
}\,.
\ee
Now let $\mathcal{Z}'$ be the TFT defined using the bicategory $\cat{L}$ as input. Then $\mathcal{Z}'(O_2)$ may likewise be computed by the composite \eqref{eq:composite_intro_o2} in $\cat{L}$, which is a $\nZ_2$-graded complex of vector spaces $Y^{\vee} \l X$ equipped with the action of a Clifford algebra. If $Y(t), X(u)$ are allowed to depend on parameters, the cut becomes a vector bundle
\be\label{eq:orynx}
\mathcal{Z}'(O_2) := Y^{\vee}(t) \l X(u)
\ee
over $\mathscr{M}_Y \times \mathscr{M}_X$ equipped with a differential and compatible Clifford action, such that
\be
\{ Y^{\vee}(t) \l X(u) \}_{P,Q} \cong Y^{\vee}(P) \l X(Q)
\ee
for every point $(P,Q)$.

@@

In forthcoming work we use the results of this paper to define a novel semantics of linear logic, in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential. Proofs in the logic are interpreted by certain correspondences between these pairs. To explain briefly why we are forced to use $\cat{L}$ rather than $\LG$, it is enough to describe the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).

Let $x$ be a variable of the logic and suppose it has denotation $\llbracket x \rrbracket = (\Spec(\nC), \nC[x], W)$ in the semantics. Let $\mathscr{M} = \mathscr{M}(W,W)$ be the affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\cat{L}$, as discussed above. Then
\begin{gather*}
\llbracket x \multimap x \rrbracket = \big(\Spec(\nC), \nC[x,x'], W(x) - W(x') \big)\,,\\
\llbracket {!}( x \multimap x ) \rrbracket = \big( \mathscr{M}, \nC, 0 \big)\,.
\end{gather*}
The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ is roughly speaking a bundle $\llbracket \underline{2} \rrbracket$ over the scheme $\mathscr{M}$ whose fiber over a loop $X$ is the square $X \l X$. More precisely, the denotation is the vector bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over a point $(X, a)$ is
\be\label{eq:bundledifferentialcliffordproof}
\llbracket \underline{2} \rrbracket_{X,a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)\,.
\ee
For these definitions to work, it is necessary to be able to compute the coefficients of $X \l X$ as a function of the coefficients of $X$, so we must use $\cat{L}$ in place of $\LG$.

@@

\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft, and to Ingo Runkel and Rafal Suszek for kindly providing Figure \ref{fig:wsh-defect}. %Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.

@@

The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$. Given potentials $W \in k[x]$ and $V \in k[y]$ the supercategory $\cat{LG}(W,V)$ is
\[
\cat{LG}(W,V) = \hmf(k[x,y], V - W)^{\oplus}\,.
\]
Given a third potential $U \in k[z]$ the composition law is a functor
\[
\LG(W,V) \otimes_k \LG(V, U) \lto \LG(W, U)
\]
which sends a pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ to the tensor product
\begin{equation}\label{eq:tensor_comp}
Y \otimes X = ( Y \otimes_{k[y]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
\end{equation}
This statement requires some care: $k[x,y,z]$ is an infinite rank free module over $k[x,z]$ and so $Y \otimes X$ is an infinite rank matrix factorisation of $U - W$ over $k[x,z]$. However one can prove that $Y \otimes X$ is a direct summand of a finite rank matrix factorisation \cite{dm1102.2957} and therefore a valid object in $\LG(W,U)$.

@@

The cut operation in $\cat{L}$ produces objects which are representations of Clifford algebras. We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}. For $n \ge 0$ the Clifford algebra $C_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $\gamma_1,\ldots,\gamma_n$ and $\gamma_1^\dagger, \ldots, \gamma_n^\dagger$ subject to the following relations
\be\label{eq:clifford_relations}
[\gamma_i, \gamma_j] = 0, \qquad [\gamma_i^\dagger, \gamma_j^\dagger] = 0, \qquad [\gamma_i, \gamma_j^\dagger] = \delta_{ij}\,.
\ee
for all $1 \le i, j \le n$. In this paper all our commutators are graded, $[a,b] = ab - (-1)^{|a||b|} ba$. We set $C_0 = k$. These Clifford algebras have essentially only one nontrivial representation, sometimes called the \emph{spinor representation} \cite[p.14]{friedrich}. To define this representation we use the $\nZ_2$-graded $k$-module
\[
F_n = k \theta_1 \oplus \cdots \oplus k \theta_n
\]
where the $\theta_i$ are formal variables of odd degree, and set
\be
S_n = \bigwedge F_n = \bigwedge\big( k \theta_1 \oplus \cdots \oplus k \theta_n \big)\,.
\ee

@@

\section{The Clifford thickening}\label{section:cliff_thick}

@@

\begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$.

The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$. This ``inflation'' produces a matrix of polynomials over $k[x,z]$. 
\end{remark}

@@

In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.

@@

\begin{remark} There is a question of whether or not the $C_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries). But Atiyah classes are independent, up to homotopy, of the choice of connection, and the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis (Lemma \ref{lemma:homotopy_indept}).
\end{remark}

>>>>

% Commands
\def\Res{\res\!}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\Ress}[1]{\res_{#1}\!}
\newcommand{\cat}[1]{\mathcal{#1}}
\newcommand{\lto}{\longrightarrow}
\newcommand{\xlto}[1]{\stackrel{#1}\lto}
\newcommand{\mf}[1]{\mathfrak{#1}}
\newcommand{\md}[1]{\mathscr{#1}}
\def\sus{\l}
\def\l{\,|\,}
\def\sgn{\textup{sgn}}

@@

\begin{abstract}
The bicategory $\LG$ of Landau-Ginzburg models has polynomials as objects and matrix factorisations as $1$-morphisms. The composition of $1$-morphisms in this bicategory naturally produces infinite rank matrix factorisations, which is a nuisance. In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
\end{abstract}

@@

If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise the possible matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$ whose coordinates are the coefficients of the various monomials in each row and column of $D$. Hence as sets we have
\begin{equation}\label{eq:param_frmf}
\LG(W,V)_{fin} = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)_{\nC}\,.
\end{equation}
For various applications, two of which we sketch below, we would like to know that the basic operations of the bicategory $\LG$ respect this additional scheme structure; that is, that these operations are continuous in the coordinates which parametrise the $1$-morphisms. The most important and nontrivial such structure is the composition functor
\begin{gather*}
\LG(V,U)_{fin} \times \LG(W, V)_{fin} \lto \LG(W,U)\,,\\
(Y,X) \mapsto Y \circ X\,.
\end{gather*}
We would like therefore to produce a morphism of schemes (omitting indices)
\[
c: \mathscr{M}(V,U) \times \mathscr{M}(W,V) \lto \mathscr{M}(W,U)
\]
with the property that $c([Y], [X]) = [Y \circ X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.

The problem is that this doesn't make sense, because the matrix of polynomials defining the composite $Y \circ X$ contains monomials $x^i y^j z^k$ with $y$'s in them and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$. However one can prove that $Y \circ X$ is a summand in the homotopy category of a finite rank matrix factorisation (involving only $x$'s and $z$'s) and even describe this object and the corresponding idempotent explicitly \cite{dm1102.2957}. This is a finite amount of data which can be used to encode $Y \circ X$, so we just need to replace $\mathscr{M}(W,U)$ by some scheme which knows how to store such data.

@@

After some refinements\footnote{See Remark \ref{remark:relation_to_toby_paper} for a discussion of why we end up encoding the finite model by Clifford actions rather than the idempotents of \cite{dm1102.2957}.} this amounts to replacing $\LG$ by an equivalent bicategory $\cat{L}$ with the same objects and (almost) the same $1$-morphisms, but whose composition operation is easily encoded as a morphism of schemes. We say \emph{almost} the same $1$-morphisms because in $\cat{L}$ the $1$-morphisms are still finite rank matrix factorisations, but now they may additionally equipped with the action of a Clifford algebra. It remains straightforward to parametrise these $1$-morphisms by the closed points of an affine scheme, but in contrast to $\LG$ the composition functor in $\cat{L}$ (which we refer to as the \emph{cut operation})
\begin{gather}
\cat{L}(V,U) \times \cat{L}(W,V) \lto \cat{L}(W,U)\,,\\
(Y,X) \mapsto Y \l X
\end{gather}
does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal. The schemes parametrising $1$-morphisms in $\cat{L}$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}. However the present paper is concerned only with defining the superbicategory $\cat{L}$ and proving that it is equivalent to $\LG$.

The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory. In Section \ref{section:lg_cut_system} we define $\cat{L}$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$.

@@

The bicategory $\LG$ arises in topological field theory (TFT) as the data necessary to define a two-dimensional topological field theory with defects \cite{k1004.2307,dkr1107.0495}. It is expected that such a TFT should be associated to any suitably nice bicategory $\cat{B}$. In the formalisation of \cite[\S 3.1]{dkr1107.0495} the associated TFT is a symmetric monoidal functor
\[
\mathcal{Z}: \operatorname{Bord}_{2,1} \lto \operatorname{Vect}_\nC
\]
where the symmetric monoidal category $\operatorname{Bord}_{2,1}$ is defined roughly as follows: the objects are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.

\begin{figure}[bt]
$$
  \raisebox{-75pt}{\begin{picture}(300,130)
  \put(0,0){\scalebox{0.6}{\includegraphics{pic02.eps}}}
  \put(0,0){
     \setlength{\unitlength}{.55pt}\put(-22,-8){
%     \put(136,224)   {$ \phi_\text{in} $}
%     \put(140, 22)   {$ \phi_\text{in} $}
%     \put(433,142)   {$ \phi_\text{out} $}
	 \put(295,190)   {$ {\scriptstyle Y} $}
	 \put(240,190)   {$ {\scriptstyle X} $}
	 \put(335,85)   {$ {\scriptstyle Z} $}
	 \put(390,105)   {$ {\scriptstyle Q} $}
     \put(510,180)   {$ O_{3} $}
     \put( 10,230)   {$ O_{1} $}
     \put( 10,110)   {$ O_{2} $}
     }\setlength{\unitlength}{1pt}}
  \end{picture}}
$$
\caption{A world-sheet $M$ with defect lines from $\,(O_1,O_2)\,$ to
$\,(O_{3})$.}
\label{fig:wsh-defect}
\end{figure}

With $\cat{B} = \LG$ an example of a morphism is given in Figure \ref{fig:wsh-defect}. The two-dimensional regions of $M$ are labelled with potentials and the defect lines are labelled with $1$-morphisms in $\LG$, that is, matrix factorisations. In the special case where we use a single label $W(x)$ for all regions, the labels $X,Y,Z,Q$ for the defect lines are all chosen from the set of $1$-morphisms $W \lto W$. The value of $\mathcal{Z}$ on $M$ is a $\nC$-linear map
\be\label{eq:value_of_bordism}
\mathcal{Z}(M): \mathcal{Z}(O_1) \otimes \mathcal{Z}(O_2) \lto \mathcal{Z}(O_3)\,.
\ee
We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$. Namely, it is a consequence of the way the defect conditions $X,Y,Z,Q$ enter the partition function (see for example \cite[(3.16)]{laz}) that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining the defect conditions. To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme parametrising possible defect conditions and $\mathcal{Z}(M)$ as a morphism of these vector bundles. But there are some obstacles.
% \cite[(2.9)]{dkr1107.0495}

Consider the incoming circle $O_2$ with two points marked $X,Y$. The construction gives
\be\label{eq:zo2orig}
\mathcal{Z}(O_2) := \Hom_{\LG(W,W)}( \Delta_W, Y^{\vee} \otimes X) \cong H^0 \Hom_{\nC[x,x']}( Y, X )
\ee
which is the vector space of $2$-morphisms $Y \lto X$ in $\LG(W,W)$. Now suppose that the defect conditions are made to depend on parameters 
\[
Y = Y(t_1,\ldots,t_r)\,, \qquad X = X(u_1,\ldots,u_s)
\]
which satisfy their own equations and cut out a parametrising scheme $\mathscr{M}_Y \times \mathscr{M}_X \subseteq \mathbb{A}^{r+s}$. The question is: what kind of global object $\mathcal{Z}(O_2)$ on $\mathscr{M}_Y \times \mathscr{M}_X$ is formed by the finite-dimensional vector spaces
\[
\mathcal{Z}(O_2)_{P,Q} := H^0 \Hom_{\nC[x,x']}( Y(P), X(Q) )
\]
as $P$ varies over $\mathscr{M}_Y$ and $Q$ over $\mathscr{M}_X$? The problem is that \emph{a priori} we have
\be\label{eq:cohom_sucks}
H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \Big\vert_{t=P, u=Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
\ee
%This is a particular case of a general phenomenon: any complex of $\nC$-vector spaces $C$ is isomorphic in the derived category $\mathbb{D}(\nC)$ to $\bigoplus_n H^n(C)[n]$, but over a general ring, for instance the coordinate ring of $\mathscr{M}_Y \times \mathscr{M}_X$, this is not the case. 
This discrepancy suggests that we should take as our global object $\mathcal{Z}(O_2)$ the Hom complex itself, as an object in the derived category\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
\be\label{eq:wuhe20}
\mathcal{Z}(O_2) := \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \in \mathbb{D}( \operatorname{qcoh} \mathscr{M}_Y \times \mathscr{M}_X )\,.
\ee
An alternative (and we believe simpler) approach is to take $\cat{L}$ rather than $\LG$ as the input to the definition of the TFT. Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define the vector space $\mathcal{Z}(O_2)$ from \eqref{eq:zo2orig} via the following composite in $\LG$:
\be\label{eq:composite_intro_o2}
\xymatrix@C+2pc{
0 \ar[r]^-X & W(x) - W(x') \ar[r]^-{Y^{\vee}} & 0
}\,.
\ee
Now let $\mathcal{Z}'$ be the TFT defined using the bicategory $\cat{L}$ as input. Then $\mathcal{Z}'(O_2)$ may likewise be computed by the composite \eqref{eq:composite_intro_o2} in $\cat{L}$, which is a $\nZ_2$-graded complex of vector spaces $Y^{\vee} \l X$ equipped with the action of a Clifford algebra. If $Y(t), X(u)$ are allowed to depend on parameters, the cut becomes a vector bundle
\be\label{eq:orynx}
\mathcal{Z}'(O_2) := Y^{\vee}(t) \l X(u)
\ee
over $\mathscr{M}_Y \times \mathscr{M}_X$ equipped with a differential and compatible Clifford action, such that
\be
Y^{\vee}(t) \l X(u) \Big\vert_{t=P,u=Q} \cong Y^{\vee}(P) \l X(Q)
\ee
for every point $(P,Q)$.

@@

In forthcoming work we will use the results of this paper to define a novel semantics of linear logic, in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential. Proofs in the logic are interpreted by certain correspondences between these pairs. To explain briefly why we are forced to use $\cat{L}$ rather than $\LG$, we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).

Let $x$ be a variable of the logic and suppose it has denotation $\llbracket x \rrbracket = (\Spec(\nC), \nC[x], W)$ in the semantics. Let $\mathscr{M} = \mathscr{M}(W,W)$ be the (indexed) affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\cat{L}$, as discussed above. Then the semantics works as follows:
\begin{gather*}
\llbracket x \multimap x \rrbracket = \big(\Spec(\nC), \nC[x,x'], W(x) - W(x') \big)\,,\\
\llbracket {!}( x \multimap x ) \rrbracket = \big( \mathscr{M}, \nC, 0 \big)\,.
\end{gather*}
The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which concretely means that $\llbracket \underline{2} \rrbracket$ is a bundle over the scheme $\mathscr{M}$ whose fiber over a loop $X$, viewed as a point $[X] \in \mathscr{M}$, is the square $X \l X$. More precisely, $\llbracket \underline{2} \rrbracket$ is the bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over $([X], a)$ is
\be\label{eq:bundledifferentialcliffordproof}
\llbracket \underline{2} \rrbracket_{[X],a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)\,.
\ee
For these definitions to work, the coefficients of the monomials in the matrix factorisation $X \l X$ need to be given explicitly as polynomial functions of the coefficients in $X$. This means we have to use $\cat{L}$ rather than $\LG$.

@@

\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft, and to Ingo Runkel and Rafal Suszek for kindly allowing the use of Figure \ref{fig:wsh-defect} from \cite{runkel}. %Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.

@@

The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$. Given potentials $W \in k[x]$ and $V \in k[y]$ the supercategory $\cat{LG}(W,V)$ is
\[
\cat{LG}(W,V) = \hmf(k[x,y], V - W)^{\oplus}\,.
\]
Given a third potential $U \in k[z]$ the composition law is a functor
\[
\LG(W,V) \otimes_k \LG(V, U) \lto \LG(W, U)
\]
which sends a pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ to the tensor product
\begin{equation}\label{eq:tensor_comp}
Y \otimes X = ( Y \otimes_{k[y]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
\end{equation}
Thus $Y \circ X := Y \otimes X$. This statement requires some care: $k[x,y,z]$ is an infinite rank free module over $k[x,z]$ and so $Y \otimes X$ is an infinite rank matrix factorisation of $U - W$ over $k[x,z]$. However one can prove that $Y \otimes X$ is a direct summand of a finite rank matrix factorisation \cite{dm1102.2957} and therefore a valid object in $\LG(W,U)$.

@@

The cut operation in $\cat{L}$ produces objects which are representations of Clifford algebras. We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}. For $n \ge 0$ the Clifford algebra $C_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $\gamma_1,\ldots,\gamma_n$ and $\gamma_1^\dagger, \ldots, \gamma_n^\dagger$ subject to the following relations
\be\label{eq:clifford_relations}
[\gamma_i, \gamma_j] = 0, \qquad [\gamma_i^\dagger, \gamma_j^\dagger] = 0, \qquad [\gamma_i, \gamma_j^\dagger] = \delta_{ij}\,.
\ee
for all $1 \le i, j \le n$. In this paper all our commutators are graded, $[a,b] = ab - (-1)^{|a||b|} ba$. We set $C_0 = k$. These Clifford algebras have essentially only one nontrivial representation, sometimes called the \emph{spinor representation} \cite[p.14]{friedrich}, defined as follows:

\begin{definition} We use the $\nZ_2$-graded $k$-module
\be
F_n = k \theta_1 \oplus \cdots \oplus k \theta_n
\ee
where the $\theta_i$ are formal variables of odd degree, and set
\be
S_n = \bigwedge F_n = \bigwedge\big( k \theta_1 \oplus \cdots \oplus k \theta_n \big)\,.
\ee
\end{definition}

@@

\subsection{The Clifford thickening}\label{section:cliff_thick}

@@

\begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$. The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$. This ``inflation'' produces a matrix of polynomials over $k[x,z]$. 
\end{remark}

@@

% In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.

@@

\begin{remark} There is a question of whether or not the $C_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$. But Atiyah classes are independent, up to homotopy, of the choice of connection.
\end{remark}
